### 2017-01-16 paper/intro.tex
pass on intro

As software evolves it is expected that the number of tests and the
length of test runs increase.  Both components can add up to the
aggregate cost of running a test suite, which can lead to late reports
of test failures.  Dealing with high testing costs is critical at
large IT organizations, with massive code and test bases.

Several approaches have been proposed in the literature to address the
regression testing problem.  Research has focused mostly on test suite
minimization, prioritization, reduction, and
selection~\cite{yoo-harman-stvr2012}.  These approaches reduce testing
cost by reducing the amount of tests for execution.  It is important
to bring to light that the \emph{complementary alternative} of
balancing the test workload across work units is sound (\ie{}, it
cannot miss fault-revealing tests) and very popular in industry.
Evidence of this are the Google TAP system~\cite{google-tap,google-ci}
and Microsoft's CloudBuild
system~\cite{prasad-shulte-ieee-microsoft-ci}, which provide
distributed infrastructures to efficienctly build massive amounts of
code and run tests.  Note, however, that the regression testing
problem is not specific to giants from the IT sector.  For example, as
of August 2013, the Groupon PWA system, which powers the
\url{groupon.com} website, included over 19K tests.  To run all those
tests under 10m, Groupon used a cluster of 4 computers with 24 cores
each~\cite{kim-etal-fse2013}.

%% As additional examples, Google's
%% TAP and Microsoft's CloudBuild distribute task workloads in the cloud.

At large organizations, the alternative of renting a cloud
service\footnote{\url{https://clutch.co/cloud}} or even building
proprietary infrastructures for running tests is a legitimate approach
to mitigate the regression testing problem.  However, for projects
with low budgets and yet moderate or heavy testing workloads, this
solution may not be economically viable.  The amount of serious
open-source project under development today is impressive.\Mar{give
  examples, provide stats.}  Optimizing existing computational
resources in this context saves money or time.  \Mar{what about free
  services (jenkins)?  how much can you scale execution and how
  expensive would that be?}

@@

\sloppy This paper focuses on the problem of understanding how
critical the regression testing problem is in open-source projects.
To the best of our knowledge no prior work investigated this problem,
which is important given the tremendous popularity of open-source
development and the wide impact of regression testing optimization
techniques in this setting.

@@

@@

>>>>

As software evolves it is expected that the number of tests and the
length of test runs increase.  Both components can add up to the
aggregate cost of running a test suite, which can lead to late reports
of test failures.  Dealing with high testing costs is important.

Several approaches have been proposed in the literature to address the
regression testing problem, with the focus mainly on test suite
minimization, prioritization, reduction, and
selection~\cite{yoo-harman-stvr2012}.  In industry, the focus has been
mainly on distributing testing workloads.  Evidence of this are the
Google TAP system~\cite{google-tap,google-ci} and Microsoft's
CloudBuild system~\cite{prasad-shulte-ieee-microsoft-ci}, which
provide distributed infrastructures to efficienctly build massive
amounts of code and run tests.  Building server clusters is also a
popular mechanism to distribute testing workloads.  For example, as of
August 2013, the Groupon PWA system, which powers the
\url{groupon.com} website, included over 19K tests.  To run all those
tests under 10m, Groupon used a cluster of 4 computers with 24 cores
each~\cite{kim-etal-fse2013}.

At large organizations, the alternative of renting a cloud
service\footnote{\url{https://clutch.co/cloud}} or even building
proprietary infrastructures for running tests is a legitimate approach
to mitigate the regression testing problem.  However, for projects
with low budgets and yet relatively heavy testing workloads, this
solution may not be economically viable.  This paper focuses on the
problem of understanding how critical the regression testing problem
is in open-source projects.  To the best of our knowledge no prior
work investigated this problem, which is becoming more important given
the tremendous popularity of open-source development.

@@

@@

\Fix{---------------- parei aqui...}

@@

\Mar{what about free services (jenkins)?  how much can you scale
  execution and how expensive would that be?}
